A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-10 doc/popl2013/intro.tex
More edits to the circuit example

\begin{lstlisting}[float={t},label={lst:circuit_ex},caption={Circuilt Simulation}]
type CircuitNode        = <float/*voltage*/,float/*current*/,
                           float/*charge*/,float/*capacitance*/>
type CircuitWire<rn,rg>  = <CircuitNode@rn,      -- Owned node
                            CircuitNode@(rn,rg), -- Owned or Ghost node
                            float/*resistance*/, float/*current*/>

>>>>

\begin{lstlisting}[float={t},label={lst:circuit_ex},caption={Circuilt Simulation}]
-- <voltage,current,charge,capacitance>
type CircuitNode        = <float,float,float,float>
-- < owned node, owned or ghost node, resistance, current>
type CircuitWire<rn,rg>  = <CircuitNode@rn, CircuitNode@(rn,rg),float,float>
